HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-09-04 scnn.tex
new todo
no line numbers by default
small edit

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}
\linenumbers

@@

%% \linenumbers

\section*{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
	\item (TK) Check use of British vs American English. Check use of tense.
	\item (TK) Larger text on figure 2. I (MD) made it one column wide instead of two as it's more an illustration than a central figure to our exposition.
	\item (MD) Figure 4: speed for multiple lmax.
    \item (TK) check part sphere notebook and whole sphere
    \item (NP) Put Raphael in the dataset author.
    \item (Probably OK) Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
    \item (I think it is OK) (NP) Check the wording. Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
    \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly. MD: lmodern is better, but can we use it (w.r.t.\ journal policy)? If equations split out, we can try to arrange them. We should also check which font size we can / have to use.
\end{itemize}

@@

A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
(i) a convolution,
(ii) a non-linearity,
(iii) a down-sampling operation,
(iv) a pooling operation, and
(v), optionally,  normalization.\footnote{\citep{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}. As operations (ii) and (v) are point-wise, they do not depend on the data domain. The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either. The convolution and down-sampling operations, however, need to be generalized from Euclidean domains to the sphere.

>>>>

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}
% \linenumbers

@@

\section*{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
	\item (TK) Check use of British vs American English. Check use of tense.
	\item (TK) Larger text on figure 2. I (MD) made it one column wide instead of two as it's more an illustration than a central figure to our exposition.
	\item (MD) Figure 4: speed for multiple lmax.
    \item (TK) check part sphere notebook and whole sphere
    \item (NP) Put Raphael in the dataset author.
	\item (NP \& MD) Move the git repository, rename the classes, check the links.
    \item (Probably OK) Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
    \item (I think it is OK) (NP) Check the wording. Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
    \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly. MD: lmodern is better, but can we use it (w.r.t.\ journal policy)? If equations split out, we can try to arrange them. We should also check which font size we can / have to use.
\end{itemize}

@@

A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
(i) a convolution,
(ii) a non-linearity,
(iii) a down-sampling operation,
(iv) a pooling operation, and
(v), optionally,  normalization.\footnote{Batch normalization has been shown to help training \citep{ioffe2015batchnorm}. We verified this experimentally in our setting as well.}
Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}. As operations (ii) and (v) are point-wise, they do not depend on the data domain. The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either. The convolution and down-sampling operations, however, need to be generalized from Euclidean domains to the sphere.
